### 2016-11-03 paper/evaluation.tex
pass on RQ1

We evaluated the characteristics of regression tests in open-source
development from a sample set of Java projects from
Github\Jbc{Remember to update the previous sentence after updating the
subject section}. We are interested in understanding the preva- lence
of long test runs, the main source of cost, and how often developers
explore parallelism to improve execution performance. We pose the
following research questions:

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
regression tests in open-source projects?}
\newcommand{\RQB}{What is the distribution of CPU and IO bound
regression tests from the sample set?}
\newcommand{\RQC}{How the execution time is distributed among test
cases?}
\newcommand{\RQD}{How often developers use the parallelism features
from build manager systems to improve performance on test execution?}

@@

The first research question addresses the distribution of subjects per
elapsed time to execute regression tests. We are interested on
identifying time-consuming test suites for further investigation. The
second research question addresses the distribution of execution time
per test case for each project. The rationale is that if the time cost
of a regression test is equally distributed among test cases, the
execution cost could be potentially improved by running tests in
parallel (in contrast to the scenario where only one test case
dominates most of the execution time).

@@

To evaluate the frequency of time-consuming regression tests, we first
compiled source and test files, later, we measured the elapsed time to
run the tests via the build system ignoring non-related tasks (\eg,
\emph{javadoc} generation).  We grouped the subjects according to the
execution time: tests that ran in less than one minute (\emph{short
execution}), one to five minutes (\emph{medium execution}), and more
than five minutes (\emph{long execution}).
Figure~\ref{fig:piechart-time} shows the proportion of subjects per
group. It is important to mention that Figure~\ref{fig:piechart-time}
represents a lower bound for elapsed time: some tests may finish early
due to a failure since the subjects were tested in a potentially
unstable revision.

>>>>

We evaluated the characteristics of regression tests in open-source
development from a sample set of Java projects from
Github\Jbc{Remember to update the previous sentence after updating the
subject section}. We are interested in understanding the prevalence
of long test runs, the main sources of cost, and how often developers
explore parallelism to improve execution performance. More
specifically, we pose the following research questions:

\newcommand{\RQA}{How prevalent is the occurence of time-consuming
regression test suites in open-source projects?}

\newcommand{\RQB}{What is the distribution of CPU and IO bound
regression tests from the sample set?}
\newcommand{\RQC}{How the execution time is distributed among test
cases?}
\newcommand{\RQD}{How often developers use the parallelism features
from build manager systems to improve performance on test execution?}

@@

The first research question addresses the distribution of subjects per
elapsed time to execute regression tests. We are interested on
identifying time-consuming test suites \Jbc{do we have a better
argument than this?}for further investigation. The
second research question addresses the distribution of execution time
per test case for each project. The rationale is that if the time cost
of a regression test is equally distributed among test cases, the
execution cost could be potentially improved by running tests in
parallel (in contrast to the scenario where only one test case
dominates most of the execution time).

@@

To evaluate the frequency of time-consuming regression tests, we
considered \Fix{X} Maven and \Fix{Y} Ant projects (\Fix{X+Y} total)
that we were able to run the tests. For each subject, we first
compiled the source and later, tested and collected the elapsed time
reported from the build system using regular expressions. To avoid
inflating the reported time, we run the tests ignoring non-related
tasks (\eg, \emph{javadoc} generation). In case of \emph{Maven}
projects, use \Jbc{How to show the following command?} \Fix{mvn test
-Dmaven.javadoc.skip=true}; in contrast, for \emph{Ant} projects, we
used \Fix{ant test} and manually inspected the test execution to
ignore any non-related tasks, if any.

We grouped the subjects according to the execution time: tests that
ran in less than one minute (\emph{short execution}), one to five
minutes (\emph{medium execution}), and more than five minutes
(\emph{long execution}). Figure~\ref{fig:piechart-time} shows the
proportion of subjects per group. It is important to mention that
Figure~\ref{fig:piechart-time} represents a lower bound for elapsed
time: some tests may finish early due to a failure since the subjects
were tested in a potentially unstable revision. \Fix{Results indicate
that a relatively high number of projects...}.
